SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2018-07-24 scipy-1.0/paper.tex
Third round of revisions for manuscript PR 34 based on reviewer feedback.

\pgfplotsset{compat=newest}
\usepackage{listings, textcomp}

\lstset{ %
  basicstyle=\ttfamily\footnotesize,  % size of fonts used for the code
  breaklines=true,   % automatic line breaking only at whitespace
  captionpos=b,   % sets the caption-position to bottom
  commentstyle=\color{gray},  % comment style
  keywordstyle=\color{blue},  % keyword style
  stringstyle=\color{red},  % string literal style
  upquote=true  %straight single quotes (requires textcomp)
}

@@

\subsection*{Statistical distributions}
Version 1.0 of SciPy saw the addition of the energy distance algorithm in
\texttt{scipy.stats.energy\_distance}. Energy distance is used in a variety
of applications ranging from genetic analysis\cite{Hu2008DetectingIC} to 
multivariate independence\cite{szekely2009}. We also added the
first Wasserstein distance algorithm to the library in
\texttt{scipy.stats.wasserstein\_distance}. The Wasserstein distance is often
used in color digital image analysis \cite{192468}.

We now provide the cumulative distribution function of the multivariate
normal distribution, \\\texttt{scipy.stats.multivariate\_normal}, via the newly
associated \texttt{logcdf} and \texttt{cdf} methods. Other recent distributions 
added to \texttt{scipy.stats} include the Argus distribution
in \texttt{scipy.stats.argus} (used in particle physics\cite{ALBRECHT1990278}), a histogram-based
distribution in \texttt{scipy.stats.rv\_histogram}, the multinomial
distribution in \texttt{scipy.stats.multinomial} (used, for example, in natural
language processing\cite{Griffiths5228}), the Burr type XII distribution in
\texttt{scipy.stats.burr12}, the skew normal distribution 
in \texttt{scipy.stats.skewnorm}, the trapezoidal distribution in 
\texttt{scipy.stats.trapz}, and the matrix normal distribution
in \texttt{scipy.stats.matrix\_normal}.

There's also a new weighted Kendall's tau statistic algorithm in
\texttt{scipy.stats.weightedtau}, and interquantile range handling in
\texttt{scipy.stats.iqr}

From a design standpoint, many functions in \texttt{scipy.stats} now support
a \texttt{nan\_policy} keyword to allow user-level control over the algorithmic
decision to propagate, omit, or raise an error in the case that \texttt{NaN}
values are encountered.

@@

\begin{lstlisting}[language=Python]
# example of a function that takes a single
# 3 dimensional typed memoryview as an argument
# this allows Cython-level handling of a NumPy
# array object
cpdef int func_new(int[:, :, :] arr):
    pass

>>>>

\pgfplotsset{compat=newest}
\usepackage{listings}

@@

\subsection*{Statistical distributions}

@@

\begin{lstlisting}[language=Python]
# example of a function that takes a single
# 3 dimesional typed memoryview as an argument
# this allows Cython-level handling of a NumPy
# array object
cpdef int func_new(int[:, :, :] arr):
    pass
